---
title       : Developing Data Products - Assignment
subtitle    : Visualise Network Utlisation
author      : Akram Faisal
job         : 
framework   : io2012       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 

## Introduction

- Generate Ramdom Poisson distibution (2 years back from today)
- Plot Histogram, Line Graph or Boxplot based on selection
- Update plot when selection changes or date range selected changes

--- .class #id

## Plot Histogram

Generated dataset and plot histogram for 2 years (daily) traffic.

```{r, echo=FALSE}
# load packages
suppressPackageStartupMessages(library(data.table))
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(googleVis)))

# Generate table for 2 years with poisson distribution
data.full <- data.table(Date = rep(Sys.Date(), 730) - seq(729, 0 , -1))
#generate new Utilisation data
data.full[, Utilisation := rpois(730, 50)]
# Ensure no values < 0 or > 100
data.full[Utilisation > 100, Utilisation := 100]
data.full[Utilisation < 0, Utilisation := 0]
# get weekdays
data.full[, Weekday := weekdays(Date, abbreviate = T)]
# Reduce weekend traffic to make it more realistic (by 50%)
data.full[Weekday %in% c("Sat", "Sun"), Utilisation := as.integer(Utilisation * 0.50)]
# Copy to data used for plotting
data <- data.full
```

```{r echo=TRUE, results = 'asis'}
hist <- gvisHistogram(as.data.frame(data$Utilisation),
                      options = list(width="100%", legend='none',
                      title="Histogram for Network Utilisation"))
print(hist, tag = 'chart')

```

---

## Plot Line 

Line graph of the network utilisation

```{r echo=TRUE, results = 'asis'}
zoom.end <- max(data$Date); zoom.start <- zoom.end - 30
line <- gvisAnnotatedTimeLine(data, datevar = "Date", numvar = "Utilisation",
                      options = list(width="90%", legend='none',
                      zoomEndTime=zoom.end, zoomStartTime=zoom.start,
                      title="Line Plot for Network Utilisation"))
print(line, tag = 'chart')
```

---

## Boxplot for Weekdays

```{r echo=TRUE, fig.width = 7, fig.height = 3, dpi = 100}
ggplot(data, aes(Weekday, Utilisation)) + geom_boxplot() +
    theme(text = element_text(size=14)) + ylim(0,100) +
    ggtitle("Network Utlisation for Weekdays")
```

Thank you